Automated detection of data fabrication using statistical tools

### 2018-04-03 submission/redraft.rmd
Add paragraph

>>>>

### Variance analysis

Sample variance- or standard deviation estimates are typically reported to indicate dispersion, but just like the mean there should be sampling error in this estimate proportional to the sample size [i.e., $\sigma/\sqrt{2n}$ under the assumption of normality, p. 351,@yule1922]. 
If an observed random variable $x$ is normally distributed, the variance of $x$ is $\chi^2$-distributed [p. 445; @hogg-tanis]; that is
$$
var(x)\sim\frac{\chi^2_{N_j-1}}{N_j-1}
$$
where $N$ is the sample size of the $j$th group. 
Using the reported summary statistics, we can compute the Mean Squares within ($MS_w$) each condition as
$$
MS_w=\frac{\sum\limits^k_{j=1}(N_j-1)s^2_j}{\sum\limits^k_{j=1}(N_j-1)}
$$
where $s^2_j$ is the variance in the $j$th group. 
The reported variances can be standardized by dividing the observed variances by the $MS_w$; we denote standardized variances with z^2$.
